\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\p}{\partial}
\newcommand{\dvar}{\,d}

% ref: http://pgfplots.sourceforge.net/gallery.html
% ref: http://tex.stackexchange.com/a/74575/79754
\usepackage{pgfplots}% This uses tikz
\pgfplotsset{compat=newest}% use newest version
\tikzset{LineStyle/.style={smooth, ultra thick, samples=400}}

% \printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
MATH 2242 - Fall 2015 - Dr. Clontz - Test 3
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill
}

\vspace{12pt}

\begin{itemize}
  \item This test is worth 250 points toward your overall grade.
        Each problem is labeled with its value toward this total. Points
        earned beyond 250 will be counted as bonus.
  \item On multiple choice problems, you do not need to show your work. No
        partial credit will be given.
  \item On full response problems, show all of your work and give a
        complete solution. When in doubt, don't skip any steps. Partial
        credit will be given at the discretion of the professor.
  \item This exam is open notes, provided that these notes are completely
        in your own handwriting. The professor may take up notes you use
        with your test and return them after the test is graded.
  \item Calculators are not necessary to solve any questions on the test and
        are not allowed.
        Notes on electronic devices must be approved by the professor
        prior to the test day (e.g. for accomodations) and should be in
        airplane mode.
  \item Tests submitted after the end of 70 minutes will be deducted 25 points,
        with 25 more points deducted every following minute.
\end{itemize}

\newpage

\begin{center}
  \textbf{Multiple Choice (110 points total)}
\end{center}

\begin{questions}

\setcounter{question}{0}
\question[20]
Find the value of the Jacobian \(\frac{\p\vect T}{\p\vect u}\) for
the affine transformation \(\vect T(u,v)=(4u-5v+7,1-2v)\).


\begin{checkboxes}
\choice \(-10\)
\choice \(0\)
\choice \(4\)
\choice \(9\)
\choice None of these
\end{checkboxes}

\vfill

\question[20]
Recall that the length of a curve is given by the path integral
\(\int_C 1\dvar s\). Which of these definite integrals
gives the circumference of the
ellipse \(\frac{x^2}{a^2}+\frac{y^2}{b^2}=1\)? Hint: use the fact that
\(\cos^2\theta+\sin^2\theta=1\).

\begin{checkboxes}
\choice \(\int_0^{2\pi}\sqrt{a^2\sin^2\theta+b^2\cos^2\theta}\dvar\theta\)
\choice \(\int_0^{2\pi}b^2-a^2\dvar\theta\)
\choice \(\int_0^{\pi}a^2\cos^2\theta+b^2\sin^2\theta\dvar\theta\)
\choice \(\int_0^{\pi}\frac{1}{\sqrt{a^2-b^2}}\dvar\theta\)
\end{checkboxes}

\vfill

\question[20]
Which of these gives the value of
\(
  \ds\int_C
    \nabla f
  \cdot\dvar\vect r
\) where \(C\) the curve given by \(\vect r(t)=(t,t^2,t^3)\) from \(t=1\)
to \(t=2\).

\begin{checkboxes}
\choice \(\operatorname{curl} \nabla f\times(\vect r(2)-\vect r(1))\)
\choice \(f(2,4,8)-f(1,1,1)\)
\choice \(\operatorname{div}\vect r(f(1,1,1))+\operatorname{div}\vect r(f(2,4,8))\)
\choice \(\vect r(2)\cdot\nabla f(1,1,1)-\vect r(1)\cdot\nabla f(2,4,8)\)
\end{checkboxes}

\vfill
\newpage

\question[20]
Express \(\int_{\p D}2xy\dvar x+xy^2\dvar y\) where \(\p D\) is the
\textbf{clockwise} oriented boundary of the unit square \([0,1]\times[0,1]\)
as a double iterated integral.
\begin{checkboxes}
  \choice \(\int_0^1\int_0^{2x}y^2+2xy+1\dvar y\dvar x\)
  \choice \(\int_0^1\int_0^1 -y^2+2x\dvar x\dvar y\)
  \choice \(\int_{-1}^0\int_{-1}^0 2xy+x+xy^2\dvar y\dvar x\)
  \choice \(\int_{-1}^1\int_{-1}^1 4y\dvar x\dvar y\)
\end{checkboxes}

\vfill

\question[20]
Let \(\vect F\) be a vector field.
Which of these is not equivalent to the rest?
\begin{checkboxes}
  \choice \(\vect F\) is conservative.
  \choice There exists a function \(f\) where \(\vect F=\nabla f\).
  \choice \(\operatorname{curl}\vect F=\vect F\).
  \choice \(\int_C\vect F\cdot\dvar\vect r\) depends only on the endpoints of \(C\).
\end{checkboxes}

\vfill

\question[10]
(BONUS)
Which of these is equal to the surface integral
\(\iint_S\<x,y,z\>\cdot\dvar\vect S\) where \(S=\{(x,y,z):x^2+y^2+z^2=1\}\)?
\begin{checkboxes}
  \choice \(\pi\)
  \choice \(3\pi\)
  \choice \(4\pi\)
  \choice \(\frac{9}{2}\pi\)
  \choice \(9\pi\)
  \choice \(0\)
  \choice None of these.
\end{checkboxes}


\end{questions}





\vfill
\newpage






\begin{center}
  \textbf{Full Response (150 points total)}
\end{center}

\begin{questions}

\setcounter{question}{6}

\question[30]
  Compute \(\iiint_W x^2+y^2+z^2\dvar V\) where
  \(W=\{(x,y,z):x^2+y^2\leq 4,0\leq z\leq 3\}\).

  \vfill



\newpage

\question[30]
  Let \(C\) be the curve \(y=e^x\) from \((1,e)\) to \((2,e^2)\).
  Prove that \(\int_C xy\dvar s=\int_1^2 xe^x\sqrt{1+e^{2x}}\dvar x\).

  \vfill



\newpage

\question[30]
  Evaluate \(\int_C \<x,y\>\cdot\dvar\vect r\) where \(C\) is the curve
  given by \(\vect r(t)=(t^2,3t)\) for \(t\in[0,1]\).

  \vfill



\newpage

\question[30]
  Evaluate \(\int_C \<yz,xz,xy\>\cdot\dvar\vect r\) where \(C\) is
  the line segment from \((1,1,1)\) to \((1,2,3)\).

  \vfill



\newpage

\question[30]
  Evaluate \(\int_C 2x\dvar y-2y\dvar x\) where \(C\) is the
  counter-clockwise oriented boundary of
  a region with area \(4\).

\end{questions}

\end{document}