\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\p}{\partial}
\newcommand{\dvar}{\,d}

% ref: http://pgfplots.sourceforge.net/gallery.html
% ref: http://tex.stackexchange.com/a/74575/79754
\usepackage{pgfplots}% This uses tikz
\pgfplotsset{compat=newest}% use newest version
\tikzset{LineStyle/.style={smooth, ultra thick, samples=400}}

% \printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
MATH 2242 - Fall 2015 - Dr. Clontz - Test 2
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill
}

\vspace{12pt}

\begin{itemize}
  \item This test is worth 250 points toward your overall grade.
        Each problem is labeled with its value toward this total. %Points
        %earned beyond 250 will be counted as bonus.
  \item On multiple choice problems, you do not need to show your work. No
        partial credit will be given.
  \item On full response problems, show all of your work and give a
        complete solution. When in doubt, don't skip any steps. Partial
        credit will be given at the discretion of the professor.
  \item This exam is open notes, provided that these notes are completely
        in your own handwriting. The professor may take up notes you use
        with your test and return them after the test is graded.
  \item Calculators are not necessary to solve any questions on the test and
        are not allowed.
        Notes on electronic devices must be approved by the professor
        prior to the test day (e.g. for accomodations) and should be in
        airplane mode.
  \item Tests submitted after the end of 70 minutes will be deducted 25 points,
        with 25 more points deducted every following minute.
\end{itemize}

\newpage

\begin{center}
  \textbf{Multiple Choice (100 points total)}
\end{center}

\begin{questions}

\setcounter{question}{0}
\question[20]
Evaluate \(\ds\int_0^1\int_{2x}^{3x-1}x\dvar y\dvar x\).


\begin{checkboxes}
\choice \(\frac{3}{2}\)
\choice \(-\frac{1}{6}\)
\choice \(3\)
\choice \(0\)
\choice None of these
\end{checkboxes}

\vfill

\question[20]
Suppose for all values of \((x,y)\in [-2,0]\times[-1,2]\) we can show that
\(1\leq f(x,y)\leq 2\). Which of these inequalities gives the best bounds
for the value of \(\iint_D f(x,y)\dvar A\)?

\begin{checkboxes}
\choice \(1\leq \iint_D f(x,y)\dvar A\leq 2\)
\choice \(\frac{1}{2}\leq \iint_D f(x,y)\dvar A\leq 4\)
\choice \(6\leq \iint_D f(x,y)\dvar A\leq 12\)
\choice \(-12\leq \iint_D f(x,y)\dvar A\leq -6\)
\choice None of these inequalities must hold.
\end{checkboxes}

\vfill
\newpage

\question[20]
Evaluate
\(
  \ds\int_0^\pi\int_0^{\pi/2}\int_0^3
    \rho^2\sin\phi
  \dvar\rho\dvar\phi\dvar\theta
\).

\begin{checkboxes}
\choice \(9\pi\)
\choice \(3\cos 1\)
\choice \(-\frac{3\pi}{2}\)
\choice \(-3\)
\choice None of these.
\end{checkboxes}

\vfill

\question[20]
Which of these Cartesian points is the same as the spherical coordinate
\(\vect s(\rho,\theta,\phi)=\vect s(2,\pi/2,\pi/3)\)?
\begin{checkboxes}
  \choice \((x,y,z)=(0,\sqrt3,1)\)
  \choice \((x,y,z)=(\pi,2,-1)\)
  \choice \((x,y,z)=(\sqrt 2,0,-\sqrt 2)\)
  \choice \((x,y,z)=(4,2\sqrt 3,2)\)
  \choice None of these
\end{checkboxes}

\vfill

\question[20]
The transformation \(\vect T:\mathbb R^2\to\mathbb R^2\) defined by
\(\vect T(x,y)=(2x+y-1,3-x)\) is which of the following?
\begin{checkboxes}
  \choice Onto and one-to-one
  \choice Onto, but not one-to-one
  \choice One-to-one, but not onto
  \choice Not onto and not one-to-one
\end{checkboxes}


\end{questions}





\vfill
\newpage






\begin{center}
  \textbf{Full Response (150 points total)}
\end{center}

\begin{questions}

\setcounter{question}{5}

\question[30]
  A barn has a rectangular base measuring \(20\) feet on the front and back,
  and \(40\) feet on the sides. The front wall is \(30\) feet high, and
  the back wall is \(40\) feet high. Express the volume of this barn as
  a double or triple iterated integral, then show that the volume is
  \(28,000\) cubic feet.

  \vfill



\newpage

\question[30]
  Evaluate \(\ds\int_0^4\int_{y/2}^2 e^{x^2}\dvar x\dvar y\).

  \vfill



\newpage

\question[30]
  Write the volume of the cone with height \(1\) and radius \(1\) as an
  iterated integral of \(x,y,z\). (Hint: use the equation \(z=\sqrt{x^2+y^2}\)).
  Do not evaluate the integral.

  \vfill



\newpage

\question[30]
  Use equations of the polar coordinates \(r,\theta\) to describe the sides
  of the triangle
  with vertices at \((x,y)=(0,0)\), \((x,y)=(2,0)\), and \((x,y)=(2,2)\).


\newpage

\question[30]
  Define an affine transformation
  taking the unit square with vertices at \((u,v)=(0,0)\),
  \((u,v)=(1,0)\), \((u,v)=(1,1)\), and \((u,v)=(0,1)\) to the parallelogram
  bounded by the lines \(y=2x\), \(y=x\), \(y=2x-1\), \(y=x+1\).

\end{questions}

\end{document}