\documentclass[12pt]{exam}

\newcommand{\ds}{\ensuremath{\displaystyle}}

\usepackage{amsmath,amsfonts, amsthm}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{harpoon}
\renewcommand{\arraystretch}{1.5}

\newcommand{\harpvec}[1]{\overrightharp{\ensuremath{\mathbf{#1}}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\p}{\partial}

% ref: http://pgfplots.sourceforge.net/gallery.html
% ref: http://tex.stackexchange.com/a/74575/79754
\usepackage{pgfplots}% This uses tikz
\pgfplotsset{compat=newest}% use newest version
\tikzset{LineStyle/.style={smooth, ultra thick, samples=400}}

% \printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
MATH 2242-090 | Spring 2016 | Dr. Clontz | Quiz 1
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill
}

\vspace{12pt}

\begin{itemize}
  \item Each quiz question is labeled with its worth toward your total quiz
        grade for the semester.
  \item On multiple choice problems, you do not need to show your work. No
        partial credit will be given.
  \item On full response problems, show all of your work and give a
        complete solution. When in doubt, don't skip any steps. Partial
        credit will be given at the discretion of the professor.
  \item This quiz is open notes and open book.
  \item This quiz is due at the end of class. Quizzes submitted over one minute
        late will be penalized by \(50\%\).
\end{itemize}

\newpage

\begin{questions}

\question[10]
Recall from the homework that \(\det(AB)=(\det A)(\det B)\).
Evaluate
\[
  \det\left(
    \left[
    \begin{matrix}
       1 &  1 \\
      -3 &  2
    \end{matrix}
    \right]
    \left[
    \begin{matrix}
       3 & -1 \\
       2 &  0
    \end{matrix}
    \right]
  \right)
\]


\begin{checkboxes}
\choice \(-9\)
\choice \(0\)
\choice \(6\)
\choice \(10\)
\choice None of these
\end{checkboxes}

\question[10]
Verify the triangle inequality
\(\|\vect x+\vect y\|\leq\|\vect x\|+\|\vect y\|\)
for \(\vect x=\<1,-2,0,2\>,\) \(\vect y=\<0,4,-3,0\>\).

\vfill
\newpage

\question[10]
Use the ``identity of Lagrange''
  \[
    \left(\sum_{i=1}^n x_iy_i\right)^2
      =
    \left(\sum_{i=1}^n x_i^2\right)
    \left(\sum_{i=1}^n y_i^2\right)
      -
    \sum_{1\leq i<j\leq n}
    \left(x_iy_j-x_jy_i \right)^2
  \]
to prove the Cauchy-Schwarz inequality
\(|\vect x\cdot\vect y|\leq\|\vect x\|\|\vect y\|\) in \(\mathbb R^n\).
(Hint: the identity of Lagrange involves the terms
\(\|\vect x\|^2,\|\vect y\|^2,|\vect x\cdot\vect y|^2\).)
\vfill
\end{questions}

\end{document}